---
title: "MA4142: Regression and Multivariate Analysis"
output: html_notebook
---
## Exploring Simple Regression
### Authors:
#### Tanmay Goyal - AI20BTECH11021, Tanay Yadav - AI20BTECH11026

- **Setting up the working directory and loading the libraries**
```{r}
setwd("C:\\Users\\tanay\\OneDrive\\Documents\\Artificial Intelligence\\Semester 6\\MA4142 Regression and Multivariate Analysis\\PPT2")

install.packages("mltools")
library(mltools)
library(data.table)
library(psych)
```

- **Reading the [Dataset](https://college.cengage.com/mathematics/brase/understandable_statistics/7e/students/datasets/slr/excel/slr02.xls)**
```{r}
data = read.csv("Crickets.csv")
data
```

The dataset predicts the number of times a cricket will chirp per second given the temperature.

- **Visualizing the dataset**
```{r}
plot( Y ~ X , data = data)
```

- **Fitting a linear model ($y = ax + b$)**
```{r}
model = lm(Y ~ X, data = data)
model
```

- **Summarizing the linear model**
```{r}
summary(model)
```

- **Visualizing the model**
```{r}
plot(Y ~ X, data=data) + abline(lm(Y ~ X, data=data) , col = 'red')
```

- **Fitting a 2nd-degree polynomial ($y = ax^2 + bx + c$)**
```{r}
model2 = lm(Y ~ X + I(X^2) , data = data)
model2
```

- **Summarizing the polynomial model**
```{r}
summary(model2)
```

- **Predicting and visualizing the polynomial model**
```{r}
pred <- predict(model2)
ix <- sort(data$X ,index.return=T)$ix

plot(data$X , data$Y) + lines(data$X[ix], pred[ix], col='red', lwd=2)
```

- **Fitting a 3rd-degree polynomial model ($y = ax^3 + bx^2 + cx + d$)**
```{r}
model3 = lm(Y ~ X + I(X^2) + I(X^3) , data = data)
model3
```

- **Summarizing the polynomial model**
```{r}
summary(model3)
```

- **Predicting and visualizing the polynomial model**
```{r}
pred <- predict(model3)
ix <- sort(data$X ,index.return=T)$ix

plot(data$X , data$Y) + lines(data$X[ix], pred[ix], col='red', lwd=2)
```

- **Fitting a 4th-degree polynomial model ($y = ax^4 + bx^3 + cx^2 + d$)**
```{r}
model4 = lm(Y ~ X + I(X^2) + I(X^3) + I(X^4) , data = data)
model4
```

- **Summarizing the model**
```{r}
summary(model4)
```
*The 4th-degree polynomial model shows a lesser r-squared value as compared to the 3rd-degree polynomial regression model.* 

- **Predicting and visualizing the polynomial model**
```{r}
pred <- predict(model4)
ix <- sort(data$X ,index.return=T)$ix

plot(data$X , data$Y) + lines(data$X[ix], pred[ix], col='red', lwd=2)
```